PCoA with bray curtis on KO abundance

### 2019-11-03 scripts/13_PCoA_brayCurtis_KO_abundance.Rmd
update

>>>>

#############################################################################

```{r}
# the PCoA of the species abundance table
spp <- read_tsv('../data/metaphlan2_result/merged_abundance_table_species.txt') %>% 
  rename_all(funs(str_replace(., '_profile$','')))

pheno <- read_csv('../data/cleaned_pheno/final_pheno.csv') %>% 
  select(-CAR_Group, -Censor_reason ) %>% 
  mutate_at(vars(str_which(names(.),'Sampleid', negate = T)), factor)

# to rearrange the cts table 
spp <- bind_cols(spp[,1],spp[,pheno$Sampleid])

# to put the feature table in the sample as rowname format to do the ML 
spp <- spp %>% 
  column_to_rownames('ID') %>% 
  as.matrix()

all.equal(colnames(spp), pheno$Sampleid)
```

```{r}
pheno_col <- pheno %>% 
  mutate(tox_col = if_else(Toxicity == 'Y', 'red', 'green '),
         CR_col = if_else(CR == 'Y', 'red', 'green '))

bc_dist <-  vegdist(t(spp), "bray")
pc_bc <- cmdscale(bc_dist, k = 2) 
plot(pc_bc[,1], pc_bc[,2], col = pheno_col$tox_col, main = 'species abundance color by tox')
plot(pc_bc[,1], pc_bc[,2], col = pheno_col$CR_col, main = 'species abundance color by CR')
```
